\documentclass{article}
\usepackage[normalem]{ulem}
\usepackage{titlesec}
\usepackage[titles]{tocloft}

%% Changing the Chapter titles to show Article instead
%\titleformat{\chapter}[display]{\Huge \bfseries}{Article \thechapter}{0.5ex} % sep
%{\Large} % before-code
%[] % after-code


\begin{document}

\title{UC Santa Cruz Amateur Radio Club \\ Bylaw Committee Report}
\author{}
\date{}
\maketitle

\section*{Members in Attendence}
Matt Carberry~~~~- KI6ELT\\
Alec Reid~~~~~~~~~~~- KM6BII\\
Stephen Petersen - AC6P
\section*{Summary}
As of Thursday May 5th, 2016, The Bylaw Committee meet to disgust changing to the Bylaw and Constitution. The committee discovered many problems in the voting process getting the 1/3 quorum together to vote on changes. One possible solution was using a voting engine to conduct elections. And the election need to happen now, they're 3 months behind schedule.
 
\section*{Proposed Changes}
\begin{enumerate}
	\item Defining the term "Total Membership" as "Total Full Membership" as shown in Article IX of the Constitution 
	\item Defining "Full Membership" as students who are active hams
	\item Expanding the Vice-Presidents role to include reporting on club events and activities.
	\item Expanding the Secretary role to include  additional responsibility to delegate duties to other member of the club. However, delegation of secretarial duties is not abdication of the responsibility of that duties. And include archival responsibility such as internet accounts, documentation, etc.  
	\item To conduct elections via secret ballot. 
	\item Add to this year ballot to change to total membership to full membership in Article IX of the constitution.
	\item Move Section 7 to Secretary role Section of the Bylaws
	\item The Treasurer would have the additional responsibility of apply for grant and other forms of funding.
\end{enumerate}


\end{document}