\documentclass{report}
\usepackage[normalem]{ulem}
\usepackage{titlesec}
\usepackage[titles]{tocloft}

%% Changing the table of contents chapter number width spacing
\renewcommand*\cftchapnumwidth{3em}

%% Changing the chapter numbers to roman
\renewcommand\thechapter{\Roman{chapter}}

%% Changing the section numbers to only show the section number
\renewcommand\thesection{\arabic{section}}

%% Changing the Chapter titles to show Article instead
\titleformat{\chapter}[display]{\Huge \bfseries}{Article \thechapter}{0.5ex} % sep
{\Large} % before-code
[] % after-code


\begin{document}

\title{UC Santa Cruz Amateur Radio Club Constitution \\ \small{Ratified March 12, 2014}}
\author{}
\date{}
\maketitle

\tableofcontents

\pagebreak

\chapter{Preamble}
We, the undersigned, wishing to secure for ourselves the pleasures and benefits of an association of persons commonly interested in Amateur Radio, constitute ourselves the\\

\indent \texttt{UCSC Amateur Radio Club (UCSC ARC)\\ \indent Of Santa Cruz, CA}\\ \\
and enact this constitution as our governing law. It shall be our purpose to further the exchange of information and cooperation between members, to promote radio knowledge, community and individual operating efficiency, and to so conduct club programs and activities as to advance the general interest and welfare of Amateur Radio in the community. 

\chapter{Membership}
All persons interested in Amateur Radio communications shall be eligible for membership. Membership shall be by application and participation upon such terms as the club shall provide in its Bylaws. Membership may not be denied because of race, creed, color, religion, gender, sexual orientation, political affiliation, marital status or any other reason that would be biased or prejudicial.
\chapter{Officers}

\section{Offices}

The officers of this club shall be President, Vice-President, Secretary, Treasurer, and Advisory Committee.

\section{Election}

The officers of this club shall be elected for a term of one year by ballot of the members    \makeatletter
      \renewcommand\l@subsection{\@dottedtocline{2}{1.5em}{3em}}
    \makeatother
 present, provided there be a quorum, at the annual meeting.

\section{Term Limits}

An individual may not hold more than one office during the same term. Term limits shall not apply.  

\section{Vacancies}

Vacancies occurring between elections must be filled by special elections at the first regular meeting following the withdrawal or resignation.

\section{Eligibility}

In order to hold an office an individual must be a UCSC student and hold a valid Amateur Radio license, excluding the Advising Committee. To hold a position on the Advising Committee, one must be a UCSC ARC Alumni, UCSC staff or faculty, or a member in good standing with the ARRL that also has an interest in the development of UCSC ARC.

\section{Resignation}

Any officer may resign his/her position in writing at which time all records and assets of the club will be turned over to the President or Vice President.

\section{Removal of Officers}

Officers may be removed from office for cause, upon written petition of six (6) or more members presented to the President or Vice President.\\

\noindent After investigation the petition will be presented to the quorum at the next regular meeting of the club and voted on by the quorum. Removal of an officer requires a two-thirds vote of the full membership.

\chapter{Duties of Officers and Standing Committees}
\section{President}

The President shall preside at all meetings, and conduct them according to the rules adopted. He/She shall enforce due observance of this Constitution and Bylaws; decide all questions of order; sign all official documents adopted by the club, and act as the official club representative in all matters related to the school of engineering. 

\section{Vice President}

The Vice-President shall assume all the duties of the President in his/her absence. In addition, he/she shall organize club activities, plan and recommend contests for operating benefits, and advance club interest and activity as approved by the club. He/She shall maintain close liaison with the local ARRL's local ARES ® Emergency Coordinator to further club participation in the Amateur Radio Emergency Service. The Vice President's responsibilities shall include forming committee positions and delegating positions to the members. If an insufficient number of members exist to fill committee positions, the responsibilities defer to the Vice President. 

\section{Secretary}

The Secretary shall keep a record of the proceedings of all meetings, keep a roll of members,  process membership applications, carry on all correspondence, read communications at each meeting, and meeting notices at least 48 hours prior to a scheduled meeting. At the expiration of his/her term he/she shall turn over all items belonging to the club to his/her successor.

\section{Treasurer}

The Treasurer shall receive and receipt for all monies paid to the club; keep an accurate account of all monies received and expended; pay no bills without proper authorization. At the end of each quarter he/she shall submit an itemized statement of disbursements and receipts. At the end of his/her term he/she shall turn over everything in his/her possession belonging to the club to his/her successor.

\section{Advisory Committee}

The purpose of the Advisory Committee is to establish a permanent representation of the UCSC Amateur Radio Club (ARC) to the Baskin School of Engineering. The Advisory Committee shall be composed of three members all of whom are either UCSC ARC Alumni, UCSC staff and faculty, or a member of good standing with the ARRL that also has an interest in the development of UCSC ARC. All three members shall have equal weight within the Advisory Committee. These officers will supplement as well as advise the other officers, especially when there is a transition to new officers.
\noindent
\chapter{Meetings}
The Bylaws shall provide for regular and special meetings. At meetings, a minimum of one-third of the membership shall constitute a quorum for the transaction of business. Robert's Rules of Order shall govern proceedings.

\chapter{Dues}
There shall be no club dues unless otherwise deemed necessary by the officers and approved by a majority vote of the total membership.

\chapter{Club Call}
The club may elect to apply for a club call sign as provided by FCC rules Part 97.\\

\noindent The President shall assign trusteeship of the club call sign.\\

\noindent The trustee shall:
\begin{itemize}
\item Be a member of the club in good standing.

\item Meet FCC requirements.

\item Not had his/her Radio Amateur licensed revoked or sanctioned at any time.
\end{itemize}

\chapter{Dissolution}
\section{Termination of Operations}

In the event that the Advisory Committee votes that the club should be dissolved the motion for dissolution must receive more than two-thirds vote of the full membership to pass.

\section{Disposition of Assets}

The Advisory Committee shall handle the disbursement of all assets of the club.

\chapter{Amendments}
This constitution or Bylaws may be amended by a two-thirds vote of the total membership. Proposals for amendments shall be submitted in writing at a regular meeting and shall be voted on at the next following regular meeting, provided all members have been noticed by mail of the intent to amend the constitution and/or By-Laws at said meeting.

\end{document}